Section Rings of $\bq$-divisors on minimal rational surfaces

### 2017-11-23 surfaces-write-up/surface-paper.tex
added in base change remark

\subsection{Notation}
Throughout, we work over a fixed algebraically closed field $\bk$.
Since generator and relation degrees are preserved under base change to the algebraic closure, 
as cohomology commutes with flat base change,
assuming that $\bk$ is algebraically closed is no restriction
on generality and the results hold equally well over an arbitrary field.

>>>>

\subsection{Notation}
\todo{move this notation subsection to its own section, after the introduction}
Throughout, we work over a fixed algebraically closed field $\bk$.
%Since generator and relation degrees are preserved under base change to the algebraic closure, 
%as cohomology commutes with flat base change,
%assuming that $\bk$ is algebraically closed is no restriction
%on generality and the results hold equally well over an arbitrary field.
\begin{rem}
	Because cohomology commutes with flat base change, in particular with field extensions,
the dimensions of the graded pieces of the section ring will be preserved under base change from $\bk$ to $\overline \bk$. Therefore generators
and relations are preserved under arbitrary base field extension, and hence their minimal degrees are preserve.
Because of this, there is not harm in assuming $\bk =\overline \bk$. The bounds we give below hold equally well
over arbitrary fields, but for simplicity we state and prove them over algebraically closed fields.

We note that canonical divisors of root stacks may not behave well with respect to base change of purely inseparable extensions,
so base change along purely inseparable extensions may cause problems if one considers 
some section ring associated to the canonical divisor.
But, for the purposes of this article, we fix a divisor on a scheme over some base field, and the structure of that particular section
ring is unchanged upon base change to the algebraic closure.
\end{rem}
